\section{Introduction}
\label{sec:introduction}
Recent advancements in signal processing and machine learning domains have resulted in an extensive surge of interest in deep learning models due to their unprecedented performance and high accuracy for different and challenging problems of significant engineering importance. We consider capsule networks (referred to as CapsNets), which are novel deep structures; recently proposed as an alternative counterpart to convolutional neural networks (CNNs), and posed to change the future of machine intelligence. \\Graphs are fundamental data structures which concisely capture the relational structure in many important real-world domains, such as knowledge graphs, physical and social interactions, language, and chemistry. Here we introduce a powerful new approach for learning generative models over knowledge graphs using CapsNet, which can capture both their structure and attributes. Our approach uses CapsNet to express probabilistic dependencies among a graph's nodes and edges, and can, in principle, learn distributions over any arbitrary graph. In a series of experiments our results show that once trained, our models can generate good quality samples of both synthetic graphs as well as real knowledge graphs, both unconditionally and conditioned on data. We also offer possible solution to key challenge of learning generative models of knowledge graphs, such as how to handle ordering of elements during the graph generation process. Our work is the first and most general approach for learning arbitrary graphs using CapsNet.